My title

### 2024-02-15 outputs/paper/paper.qmd
editing

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Mary Cheng
  - Shipeng Zhang
  - Yimiao Yuan
thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers some insights into the regional variations and the overall prevalence of bullying concerns. By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges. The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches. The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume. The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying.
